6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-22 paper.tex
FINAL ASPELL

 Infrastructure complexity is steadily increasing, and is a leading cause of downtime and unreliability. According to a recent Gartner survey, 73\% of IT executives say their infrastructure complexity is either `high' or `out of control'~\cite{Gartner2013}.

@@

Languages and tools for the modelling of software architecture and infrastructure do exist, however they lack the simplicity and pragmatism in their implementation to see widespread adoption in industry~\cite{ModellingAdoption}. I propose a simple, pragmatic tool that may come with some modelling limitations, but will be quick and easy to set up and begin reaping the benefits.

@@

Studies into increased quality, maintainability and developer productivity when using MDSE techniques can be found commonly in academia but are difficult to find in industry. In a study into Industrial Adoption of Model Driven Development, it was stated that "interviewees emphasised tool immaturity, complexity and lack of usability as major barriers to adoption"~\cite{IndustryMDSE}.

@@

The real value of these DSL's is that they are directly executable.  They can be executed to drive infrastructure changes and ensure convergence with the model. Figure~\ref{fig:PuppetDSLSnippet} provides an example snippet of a Puppet recipe, declaratively specifying details of the SSH (secure shell) service that will be made available on a specific host.

@@

    This query can become expensive, with a time complexity on the order of $O(n^3)$, therefore it uses a common time-space tradeoff technique known as `materialized views'\footnote{For more details on materialized views, see http://www.postgresql.org/docs/9.3/static/rules-materializedviews.html} to incrementally compute changes over time. The total number of nodes is usually low enough to make this feasible.
  \item The failing service or component is defined as the root cause if:
    \begin{enumerate}
      \item It has no failing dependencies itself.
      \item There is a dependency path to it from all other failing services/components.
    \end{enumerate}
\end{enumerate}

@@

@@

\begin{description}
  \item[Rendering]
    Most web applications are executed exclusively on the server-side, this is an obvious choice as it provides many benefits such as: low-latency database access, the standard execution environment of a server under the developers control and improved security, eg.\ no direct database access or ability to modify the source code. With a single page application, the server side components are usually exposed via an API which takes advantage of these benefits, and the client-side JavaScript fetches data from this API via AJAX requests. When data is received, it is rendered into HTML elements by JavaScript executing in the browser.
  \item[Interactivity and Responsiveness]
    The user experience of a single page application can be significantly better than a traditional website, when used in an appropriate situation. Websites can feel much more like a native desktop application, with multiple views, background data synchronisation, data filtering etc. The main increase in responsiveness comes from eliminating page reloads, which incur the full latency penalty unless they are cached, thereby increasing perceived performance.
  \item[Deep Linking \& History]
    Browsers cater well to traditional web pages, as each page must have a uniquely accessible URL and is explicitly navigated to by clicking on a hyperlink. Single page applications must emulate this behaviour using JavaScript techniques to achieve deep-linking so that bookmarks or shared URL's will navigate to the correct state within an application. Features such as the HTML5 history API enable this.
  \item[Search Engine Optimisation]
    Single Page Applications are generally a poor choice where search engine rankings are important for a website. Search crawlers typically do not execute JavaScript and are therefore unable to index content effectively. For a tool such as the Monitoring UI, this is unimportant, as it is intended as an internal tool which will often be protected by a layer of authentication and not accessible from the web. Solutions for this issue are available, and involve executing the application on the server side using a JavaScript engine such as Node.js initially.
  \item[ Abstraction and Maintainability]
    Single page application frameworks often apply standard architectural patterns such as Model-View-Controller. These patterns can help to raise the level of abstraction when creating highly interactive applications beyond manually binding event listeners to DOM elements in order to update and present data. Applications that are abstracted from the imperative nature of programming with the DOM (Document Object Model) can find benefits in a more declarative approach. This can help improve testability, code reuse and can reduce the number of defects.
\end{description}

@@

\begin{description}
  \item[Check Flexibility] The ability to check arbitrary properties of a system from a black box perspective (without access to the source code) can be seen as a significant benefit of using this tool.
  \item[Effective Visualization \& Communication] Perhaps the largest improvement over existing monitoring tools such as Nagios is the quality of visualisation. Service specifications generate easy to understand architecture diagrams of dependencies, with live updates when the state of each component changes. The extra context that this provides means that operations teams will be better placed to understand the modelled systems and the impact of problems whenever they occur.
  \item[Root Cause Analysis] Whilst the root cause analysis mechanism is quite simple, it has proven to be effective in narrowing down the scope of problems, especially in more complex systems and therefore aiding in their resolution. Most other monitoring tools lack the context to be able to do this kind of analysis.
\end{description}

>>>>

 Infrastructure complexity is steadily increasing, and is a leading cause of downtime and unreliability. According to a recent Gartner survey, 73\% of IT executives say their infrastructure complexity is either `high' or `out of control'.

@@

Languages and tools for the modelling of software architecture and infrastructure do exist, however they lack the simplicity and pragmatism in their implementation to see widespread adoption in industry~\cite{IndustryMDSE}. I propose a simple, pragmatic tool that may come with some modelling limitations, but will be quick and easy to set up and begin reaping the benefits.

@@

Studies into increased quality, maintainability and developer productivity when using MDSE techniques are found commonly in academia but are difficult to find in industry. In a study into Industrial Adoption of Model Driven Development, it was stated that ``interviewees emphasised tool immaturity, complexity and lack of usability as major barriers to adoption"~\cite{IndustryMDSE}.

@@

The real value of these DSL's is that they are directly executable.  They can be executed to drive infrastructure changes and ensure convergence with the model. Listing~\ref{fig:PuppetDSLSnippet}. provides an example snippet of a Puppet recipe, declaratively specifying details of the SSH (secure shell) service that will be made available on a specific host.

@@

@@

    This query can become expensive, with a time complexity on the order of $O(n^3)$, therefore it uses a common time-space trade-off technique known as `materialized views'\footnote{For more details on materialized views, see http://www.postgresql.org/docs/9.3/static/rules-materializedviews.html} to incrementally compute changes over time. The total number of nodes is usually low enough to make this feasible.
  \item The failing service or component is defined as the root cause if:
    \begin{enumerate}
      \item It has no failing dependencies itself.
      \item There is a dependency path to it from all other failing services/components.
    \end{enumerate}
\end{enumerate}

@@

\begin{description}
  \item[Rendering]
    Most web applications are executed exclusively on the server-side, this is an obvious choice as it provides many benefits such as: low-latency database access, the standard execution environment of a server under the developers control and improved security, eg.\ no direct database access or ability to modify the source code. With a single page application, the server side components are usually exposed via an API which takes advantage of these benefits, and the client-side JavaScript fetches data from this API via AJAX requests. When data is received, it is rendered into HTML elements by JavaScript executing in the browser.
  \item[Interactivity and Responsiveness]
    The user experience of a single page application can be significantly better than a traditional website, when used in an appropriate situation. Websites can feel much more like a native desktop application, with multiple views, background data synchronisation, data filtering etc. The main increase in responsiveness comes from eliminating page reloads, which incur the full latency penalty unless they are cached, thereby increasing perceived performance.
  \item[Deep Linking \& History]
    Browsers cater well to traditional web pages, as each page must have a uniquely accessible URL and is explicitly navigated to by clicking on a hyperlink. Single page applications must emulate this behaviour using JavaScript techniques to achieve deep-linking so that bookmarks or shared URL's will navigate to the correct state within an application. Features such as the HTML5 history API enable this.
  \item[Search Engine Optimisation]
    Single Page Applications are generally a poor choice where search engine rankings are important for a website. Search crawlers typically do not execute JavaScript and are therefore unable to index content effectively. For a tool such as the Monitoring UI, this is unimportant, as it is intended as an internal tool which will often be protected by a layer of authentication and not accessible from the web. Solutions for this issue are available, and involve executing the application on the server side using a JavaScript engine such as Node.js initially.
  \item[ Abstraction and Maintainability]
    Single page application frameworks often apply standard architectural patterns such as Model-View-Controller. These patterns can help to raise the level of abstraction when creating highly interactive applications beyond manually binding event listeners to Document Object Model (DOM) elements in order to update and present data. Applications that are abstracted from the imperative nature of programming with the DOM can find benefits in a more declarative approach. This can help improve testability, code reuse and can reduce the number of defects.
\end{description}

@@

\begin{description}
  \item[Check Flexibility] The ability to check arbitrary properties of a system from a black box perspective (without access to the source code) can be seen as a significant benefit of using this tool.
  \item[Effective Visualisation \& Communication] Perhaps the largest improvement over existing monitoring tools such as Nagios is the quality of visualisation. Service specifications generate easy to understand architecture diagrams of dependencies, with live updates when the state of each component changes. The extra context that this provides means that operations teams will be better placed to understand the modelled systems and the impact of problems whenever they occur.
  \item[Root Cause Analysis] Whilst the root cause analysis mechanism is quite simple, it has proven to be effective in narrowing down the scope of problems, especially in more complex systems and therefore aiding in their resolution. Most other monitoring tools lack the context to be able to do this kind of analysis.
\end{description}
